---
title: "Study 2"
author: "Authors"
date: "2022-10-18"
output: html_document
---

#Installing packages
```{r}
install.packages("tidyverse")
install.packages("sjPlot")
install.packages("cowplot")
install.packages("haven")
```

#Loading packages
```{r}
library(tidyverse)
library(sjPlot)
library(cowplot)
library(haven)
```

#Loading the data file
```{r}
d <- read_sav("/Users/toroklilla/Dropbox/Mac/Desktop/Study_2.sav")
```

#Preparing and checking variables before analyses
```{r}
d$Condition <- as.factor(d$Condition)
d$Condition <-
  recode_factor(d$Condition, `1` = "Fixed Mindset", `2` = "Growth Mindset")
table(d$Condition)

d$SH_cat <- as.factor(d$SH_cat)
d$SH_cat <-
  recode_factor(d$SH_cat, `0` = "Not Selected
  Debilitating Music", `1` = "Selected
  Debilitating Music")
table(d$SH_cat)

d$Gender <- as_factor(d$Gender)
d$Gender <- recode_factor(d$Gender, `1` = "Male", `2` = "Female", `3` = "Other")
table(d$Gender)

d$Challenge <- as.factor(d$Challenge)
d$Challenge <-
  recode_factor(d$Challenge, `0` = "Did not Explain with Challenge Seeking", `1` = "Explained with Challenge Seeking")
table(d$Challenge)

d$Curiosity <- as.factor(d$Curiosity)
d$Curiosity <-
  recode_factor(d$Curiosity, `0` = "Did not Explain with Curiosity", `1` = "Explained with Curiosity")
table(d$Curiosity)

d$Curiosity_music <- as.factor(d$Curiosity_music)
d$Curiosity_music <-
  recode_factor(d$Curiosity_music, `0` = "Did not Explain with Curiosity to the Music", `1` = "Explained with Curiosity to the Music")
table(d$Curiosity_music)

d$Curiosity_self <- as.factor(d$Curiosity_self)
d$Curiosity_self <-
  recode_factor(d$Curiosity_self, `0` = "Did not Explain with Curiosity to Themselves", `1` = "Explained with Curiosity to Themselves")
table(d$Curiosity_self)

d$univ <- as.factor(d$University)
d$univ <-
  recode_factor(d$univ, `1` = "Science
  University", `2` = "Sports
  University")
table(d$univ)
```

#Creating models with control variables (gender, condition and university type)
```{r}
mod <-
  glm(Curiosity ~ SH_cat + Gender + Condition + univ,
      family = "binomial",
      data = d)
summary(mod)
tab_model(mod, show.stat = T, use.viewer = T)

mod2 <-
  glm(Curiosity_music ~ SH_cat + Gender + Condition + univ,
      family = "binomial",
      data = d)
summary(mod2)
tab_model(mod2, show.stat = T, use.viewer = T)

mod3 <-
  glm(Curiosity_self ~ SH_cat + Gender + Condition + univ,
      family = "binomial",
      data = d)
summary(mod3)
tab_model(mod3, show.stat = T, use.viewer = T)
```

#Creating models without control variables (gender, condition and university type)
```{r}
mod1 <-
  glm(Curiosity ~ SH_cat,
      family = "binomial",
      data = d)
summary(mod1)
tab_model(mod1, show.stat = T, use.viewer = T)

mod2 <-
  glm(Curiosity_music ~ SH_cat,
      family = "binomial",
      data = d)
summary(mod2)
tab_model(mod2, show.stat = T, use.viewer = T)

mod3 <-
  glm(Curiosity_self ~ SH_cat,
      family = "binomial",
      data = d)
summary(mod3)
tab_model(mod3, show.stat = T, use.viewer = T)
```

##Plotting models
```{r}
plot1 <-
  plot_model(
    mod1,
    type = "pred",
    terms = "SH_cat",
    colors = "gs",
    align = c("v"),
    title = "A",
    axis.title = c("", "Curiosity Overall % of Participants")
  ) +
  geom_bar(
    position = position_dodge(),
    stat = "identity",
    width = 0.5,
    alpha = 0.7
  ) +
  coord_cartesian(ylim = c(0, 1)) +
  scale_fill_grey() +
  theme_classic()

plot2 <-
  plot_model(
    mod2,
    type = "pred",
    terms = "SH_cat",
    colors = "gs",
    align = c("v"),
    title = "B",
    axis.title = c("", "Curiosity to Music")
  ) +
  geom_bar(
    position = position_dodge(),
    stat = "identity",
    width = 0.5,
    alpha = 0.7
  ) +
  coord_cartesian(ylim = c(0, 1)) +
  scale_fill_grey() +
  theme_classic()

plot3 <-
  plot_model(
    mod3,
    type = "pred",
    terms = "SH_cat",
    colors = "gs",
    align = c("v"),
    title = "C",
    axis.title = c("", "Curiosity to the Self")
  ) +
  geom_bar(
    position = position_dodge(),
    stat = "identity",
    width = 0.5,
    alpha = 0.7
  ) +
  coord_cartesian(ylim = c(0, 1)) +
  scale_fill_grey() +
  theme_classic()

plot_fig <-
  plot_grid(
    plot1,
    plot2,
    plot3,
    align = c("h"),
    scale = 1,
    ncol = 3,
    nrow = 1
  )

plot_fig
```

#Supplementary material: testing the effect of university type on explaining self-handicapping
```{r}
mod4 <-
  glm(
    Curiosity ~ univ + Gender + Condition,
    family = "binomial",
    data = d,
    subset = SH_cat == "Selected
  Debilitating Music"
  )
summary(mod4)
tab_model(mod4, show.stat = T, use.viewer = T)

mod5 <-
  glm(
    Challenge ~ univ + Gender + Condition,
    family = "binomial",
    data = d,
    subset = SH_cat == "Selected
  Debilitating Music"
  )
summary(mod5)
tab_model(mod5, show.stat = T, use.viewer = T)
```

##Supplementary material: plotting the models testing the effect of university type on self-handicapping explanation
```{r}
plot4 <-
  plot_model(
    mod4,
    type = "pred",
    terms = "univ",
    colors = "gs",
    align = c("v"),
    title = "A",
    axis.title = c("", "% of Self-Handicappers Reporting Curiosity")
  ) +
  geom_bar(
    position = position_dodge(),
    stat = "identity",
    width = 0.5,
    alpha = 0.7
  ) +
  coord_cartesian(ylim = c(0, 1)) +
  scale_fill_grey() +
  theme_classic()

plot5 <-
  eg1 <-
  plot_model(
    mod5,
    type = "pred",
    terms = "univ",
    colors = "gs",
    align = c("v"),
    title = "B",
    axis.title = c("", "% of Self-Handicappers Reporting Challenge Seeking")
  ) +
  geom_bar(
    position = position_dodge(),
    stat = "identity",
    width = 0.5,
    alpha = 0.7
  ) +
  coord_cartesian(ylim = c(0, 1)) +
  scale_fill_grey() +
  theme_classic()

plot_uni <-
  plot_grid(
    plot4,
    plot5,
    align = c("h"),
    scale = 1,
    ncol = 2,
    nrow = 1
  )

plot_uni
```